Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-21 tex/main/manuscript.tex
梳理完结果部分

Some main drivers caused the changes of water utilization regime (Figure\ref{fig:Causes}).
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are key to the
changes in the tendentiousness of water utilization in P1 and P2.
During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
and agriculture was the dominant water use (xx \% of the total).
After entering P2, however, while the expansion of irrigated area stalled, 
industry and services gradually took off, which took up more water resources.
% 用水关系的变化
(2) Efficiency of water use sparkly changed during the P3.
Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
both their output per unit and water consumption per unit area experienced significant declines.
As a result, after the P3, the proportions of the different water-using sectors tend to average out 
while the total water consumption remains stable.
% 不断变化的管理模式。
(3) Changing water management practice contributed between different periods.
In P1, most of the reservoirs are built in regions where water use is growing, 
and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
In P2, on the other hand, the number of additional reservoirs decreases significantly. 
Within P3, the number of reservoirs increases significantly again, 
but the growth of storage capacity does not match the growth of water demand.

>>>>

Some main drivers caused the above changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are keys to the changes in the tendentiousness of water utilization between P1 and P2 (Figure\ref{fig:Causes} A). During the P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of $0.25*10^6/year$, and irrigation water was the dominant utilization way ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978). Entering P2, however, while the expansion of irrigated area stalled, industry and services gradually took off and took up more water resources (Figure\ref{fig:Causes} B), leading to $8\%$ reduction of proportion of irrigation water.

% 用水关系的变化
(2) During the P3, irrigation, whose water consumptions were still dominating, have noticeable changes in its efficiency, however. Although irrigated agricultural area resumed expansion, and both industry, urban services were boosting their gross added values (GVA), water use density (WUI) experienced significant declines and reached the lowest points (Figure\ref{fig:Causes} A and B). It means, water utilization ways  have changed, along with technological solutions and a range of water conservation practices (supplementary Fig. S6). As a result, the proportions of water use between the different sectors tend to average out while the total water consumption remains stable, after the P3 (supplementary Fig. S7).

% 不断变化的管理模式。
(3) Changing water management practice contributed throughout all three periods. In the P1, most of the reservoirs are built in regions with high water demands, as ratio of regional water use and basinal water use for each new reservoir are significantly higher (Figure~\ref{fig:Causes}C). In the P2, on the other hand, the number of new reservoirs decreases significantly with little increment of total storage capacities (supplementary Fig. S5). Entering the P3, however, the number of new reservoirs are even much higher than that in the P1, and most of them were built in regions with lower ratio of regional water use and basinal water use (Figure~\ref{fig:Causes}C and supplementary Fig. S5).

### 2020-08-21 tex/sup/PNAS-template-main.tex
订正了所有正文的图
梳理完结果部分

>>>>

% 补充图片6：节水措施
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{../../figures/placeholder_l.jpg}
    \caption{technological solutions and water conservation practices}
\end{figure}

% 补充图片7：用水比例
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../../figures/supplementary_information/sf_wu_sections_stackplot.jpg}
    \caption{Proportions of water use between the different sectors}
\end{figure}

% 补充图片X：管理政策
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{../../figures/supplementary_information/managements.pdf}
    \caption{Number of management practices in different periods, including policy and reservoirs.}
\end{figure}
